### 2013-03-21 analysis/01GlobalRegression/GlobalRegression.Rmd

```{r}
library(foreign)
require(zoo)
require(lmtest)
require(car)
workingdata20052010 <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010.dbf")
workingdata20052010.Dakota <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010_Dakota.dbf")
model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + MAX + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
model.SaleValue20052010.Dakota <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX * I(CBD_dist ^2)+ MAX*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO+BEDS + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata20052010.Dakota)
mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["MAX"]) * (workingdata20052010$SALE_VALUE)
mfx.LAND.20052010 = (model.SaleValue20052010$coefficients["ACRES_POLY"]+ (2*workingdata20052010$ACRES_POLY * model.SaleValue20052010$coefficients["I(ACRES_POLY^2)"])+
  (model.SaleValue20052010$coefficients["ACRES_POLY:CBD_dist"]*workingdata20052010$CBD_dist) + (model.SaleValue20052010$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata20052010$CBD_dist ^2)) + 
  (model.SaleValue20052010$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata20052010$CBD_dist*workingdata20052010$ACRES_POLY)+
  (model.SaleValue20052010$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010$ACRES_POLY*(workingdata20052010$CBD_dist ^2))) * (workingdata20052010$SALE_VALUE)
mfx.TRAFFIC.20052010.Dakota = ((model.SaleValue20052010.Dakota$coefficients["MAX"])+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota$coefficients["CBD_dist:MAX"])+
  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota$coefficients["I(CBD_dist^2):MAX"])))) * (workingdata20052010.Dakota$SALE_VALUE)
mfx.LAND.20052010.Dakota = (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY"]+ (2*workingdata20052010.Dakota$ACRES_POLY * model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2)"])+
  (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY:CBD_dist"]*workingdata20052010.Dakota$CBD_dist) + (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata20052010.Dakota$CBD_dist ^2)) + 
  (model.SaleValue20052010.Dakota$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata20052010.Dakota$CBD_dist*workingdata20052010.Dakota$ACRES_POLY)+
  (model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010.Dakota$ACRES_POLY*(workingdata20052010.Dakota$CBD_dist ^2))) * (workingdata20052010.Dakota$SALE_VALUE)

@@

```{r}
summary(model.SaleValue20052010)
summary(model.SaleValue20052010.Dakota)
```

@@

```{r}
#Traffic Noise
summary(mfx.TRAFFIC.20052010)
summary(mfx.TRAFFIC.20052010.Dakota)
#Land Size
summary(mfx.LAND.20052010)
summary(mfx.LAND.20052010.Dakota)
```

>>>>

```{r}
library(foreign)
require(zoo)
require(lmtest)
require(car)
workingdata20052010 <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010.dbf")
workingdata20052010.Dakota <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010_Dakota.dbf")
model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + MAX + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
model.SaleValue20052010.Dakota <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX * I(CBD_dist ^2)+ MAX*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO+BEDS + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata20052010.Dakota)
mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["MAX"]) * (workingdata20052010$SALE_VALUE)
mfx.LAND.20052010 = (model.SaleValue20052010$coefficients["ACRES_POLY"]+ (2*workingdata20052010$ACRES_POLY * model.SaleValue20052010$coefficients["I(ACRES_POLY^2)"])+
  (model.SaleValue20052010$coefficients["ACRES_POLY:CBD_dist"]*workingdata20052010$CBD_dist) + (model.SaleValue20052010$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata20052010$CBD_dist ^2)) + 
  (model.SaleValue20052010$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata20052010$CBD_dist*workingdata20052010$ACRES_POLY)+
  (model.SaleValue20052010$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010$ACRES_POLY*(workingdata20052010$CBD_dist ^2))) * (workingdata20052010$SALE_VALUE)
mfx.TRAFFIC.20052010.Dakota = ((model.SaleValue20052010.Dakota$coefficients["MAX"])+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota$coefficients["CBD_dist:MAX"])+
  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota$coefficients["I(CBD_dist^2):MAX"])))) * (workingdata20052010.Dakota$SALE_VALUE)
mfx.LAND.20052010.Dakota = (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY"]+ (2*workingdata20052010.Dakota$ACRES_POLY * model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2)"])+
  (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY:CBD_dist"]*workingdata20052010.Dakota$CBD_dist) + (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata20052010.Dakota$CBD_dist ^2)) + 
  (model.SaleValue20052010.Dakota$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata20052010.Dakota$CBD_dist*workingdata20052010.Dakota$ACRES_POLY)+
  (model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010.Dakota$ACRES_POLY*(workingdata20052010.Dakota$CBD_dist ^2))) * (workingdata20052010.Dakota$SALE_VALUE)
model.SaleValue20052010.Dakota.NoBeds <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX * I(CBD_dist ^2)+ MAX*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO, data=workingdata20052010.Dakota)
mfx.TRAFFIC.20052010.Dakota.NoBeds = ((model.SaleValue20052010.Dakota.NoBeds$coefficients["MAX"])+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota.NoBeds$coefficients["CBD_dist:MAX"])+
  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota.NoBeds$coefficients["I(CBD_dist^2):MAX"])))) * (workingdata20052010.Dakota$SALE_VALUE)

@@

```{r}
summary(model.SaleValue20052010)
summary(model.SaleValue20052010.Dakota)
summary(model.SaleValue20052010.Dakota.NoBeds)
```

@@

```{r}
#Traffic Noise
summary(mfx.TRAFFIC.20052010)
summary(mfx.TRAFFIC.20052010.Dakota)
summary(mfx.TRAFFIC.20052010.Dakota.NoBeds)
#Land Size
summary(mfx.LAND.20052010)
summary(mfx.LAND.20052010.Dakota)
```
